State-space age-structured assessment models provide reliable inferences(?)

### 2022-07-25 Project_0/paper/paper.Rmd
fix yet another error in M oms
make naa oms consistent before redoing sims
fix em inputs, selectivity oms

---
title: State-space age-structured assessment models provide reliable inferences(?)
author: 
  - Timothy J. Miller^1^
date: ''
fontsize: 12pt
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    includes:
      in_header:
      - options.sty
      - journalshortcuts.tex
    keep_tex: yes
    number_sections: yes
  html_document:
    df_print: paged
  word_document: default
header-includes:
- \usepackage{xspace}
- \usepackage{bm}
- \usepackage{caption,graphics}
- \usepackage{graphicx}
- \usepackage{makecell}
- \renewcommand\figurename{Fig.}
- \captionsetup{labelsep=period, singlelinecheck=false}
- \newcommand{\changesize}[1]{\fontsize{#1pt}{#1pt}\selectfont}
- \renewcommand{\arraystretch}{1.5}
- \renewcommand\theadfont{}
csl: canadian-journal-of-fisheries-and-aquatic-sciences.csl
biblio-style: cjfas2.bst
---

@@

@@

We completed a simulation study with 24 NAA re operating models, 16 M re operating models, X Sel re operating models and Y q re operating models. 
We simulated N data sets for each operating model.
For each simulated data from each operating model we fit a set of estimating models.

@@

@@

@@

Convergence performance

@@

>>>>

---
title: State-space age-structured assessment models provide reliable inferences(?)
author: 
  - Timothy J. Miller^1^, Britten, Brooks, Fay, Legault, Stock, 
date: ''
fontsize: 12pt
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    includes:
      in_header:
      - options.sty
      - journalshortcuts.tex
    keep_tex: yes
    number_sections: yes
  html_document:
    df_print: paged
  word_document: default
header-includes:
- \usepackage{xspace}
- \usepackage{bm}
- \usepackage{caption,graphics}
- \usepackage{graphicx}
- \usepackage{makecell}
- \renewcommand\figurename{Fig.}
- \captionsetup{labelsep=period, singlelinecheck=false}
- \newcommand{\changesize}[1]{\fontsize{#1pt}{#1pt}\selectfont}
- \renewcommand{\arraystretch}{1.5}
- \renewcommand\theadfont{}
csl: canadian-journal-of-fisheries-and-aquatic-sciences.csl
biblio-style: cjfas2.bst
---

@@

Much is known about the reliabiltiy of state-space models that are linear or Gaussian, but applications in fisheris management are
nonlinear and typically include multiple types of observations with varying distributional assumptions. We know relatively little about
the statistical reliability of such models. Also, there is a wide range of potential random effects structures in assessment models
and we  know little about the ability of information criteria to distinguish among such alternative structures.

But those studies focus primarily on Gaussain 
Reliability of hidden process models

@@

Used the WHAM package commit = XXXXXXX (Stock and Miller 2021, Miller and Stock 2020). This packages has also been used
to configure operating and estimating models for closed loop simulations evaluating index-based asssessment methods (Legault et al. In press).

We completed a simulation study with 24 NAA re operating models, 16 M re operating models, 16 Sel re operating models and 16 q re operating models. 
We simulated N data sets for each operating model.
For each simulated data from each operating model we fit a set of estimating models.

@@

marginal standard deviations for random effects are defined in tables of operating models.

@@

Make plot of S-R curve, Fmsy = F40
Initial values for BH parameters are the true values.
Initial values for mean R model = true R0.

@@

Do each of these by type of operating model (Naa, M, sel, q)
Convergence performance

@@

The estimating models assumed variances of aggregate catch and index observations was known. This approximation may be appropriate for indices
where we have a reliable estimate of uncertainty based on the survey design (), but there may be better approaches for the aggregate
catch such as an informed prior on the standard errors with realistic bounds.
